Complementing theory on adolescent emotion regulation using  machine learning

### 2022-02-24 manuscript/manuscript.Rmd
update 2022-02-24 12:38:04

---
title             : "Complementing theory on adolescent emotion regulation using data-driven insights from machine learning"
shorttitle        : "Title"

@@

```{r setup, include = FALSE}
library("papaja")
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
```

@@

Empirical support for this notion of diverging destinies is evident from studies that examine developmental trajectories of emotion regulation in adolescence: 
Such studies consistently reveal large between-individual heterogeneity [see @craccoEmotionRegulationChildhood2017; @vanlissaRoleFathersMothers2019; @zimmermannEmotionRegulationEarly2014; @reindlSocializationEmotionRegulation2016].
An important next step is to identify which risk factors render some adolescents susceptible to emotion dysregulation.
<!-- This goal fits within the paradigm shift that has gripped the field of pedagogy, towards “person-centered” research, which focuses on individual developmental trajectories and within-family predictive processes, rather than average patterns across samples16,23. Seminal studies have applied “clustering” methods to identify youth with similar developmental trajectories14,24–26. Adolescents may follow similar trajectories for different reasons, however, and person-centered methods are too complex to accommodate more than a handful of theoretically-derived predictors. Unfortunately, relevant theory on adolescent emotion regulation development is limited27–29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30. -->

@@

<!-- Maybe review theory briefly? -->
The first step towards theory formation or revision is identifying relevant phenomena [@borsboomTheoryConstructionMethodology2020].
Thus, offering a starting point for this endeavor,<!-- empirical investigations of predictors of adolescents' emotion regulation development -->
a recent literature review 
used a new method, the text mining systematic review, to identify relevant phenomena in relation to adolescents' emotion regulation based on the analysis of author keywords and abstracts of 6305 publications  [@vanlissaMappingPhenomenaRelevant2021].
Typically, phenomena are identified using narrative literature reviews.
However, these are often limited to a small number of papers and structured around well-established ideas [@littellEvidencebasedBiasedQuality2008]
Text mining systematic reviews, by comparison, are relatively comprehensive and derive insights from the literature through a relatively transparent and objective - albeit less interpretative - procedure [@vanlissaMappingPhenomenaRelevant2021]. <!-- reflection and meaning-making-->

@@

<!-- Deductive research, or hypothesis-testing, is the predominant focus of contemporary behavioral research. It tends to focus on a relatively narrow set of theoretically-derived variables, and the results revolve around statistical inference: Whether the theoretical hypotheses are supported by significant or reliable effects. In deductive research, less emphasis is placed on comprehensiveness or breadth of candidate predictors. Relatedly, the relative importance of different predictors is often of secondary importance, as is the model’s predictive performance. Thus, although an advantage of deductive approaches is that they can be used to draw inferences about theoretical hypotheses, they also have specific limitations.  -->
<!-- To allocate scientific resources effectively, it is important to cast a wide net among potential predictors, across different theories, and even include under-theorized factors to unearth potential blind spots in the extant literature. Inductive research – that is, rigorous exploratory work that identifies reliable patterns in data, is more suited to these demands.  -->
<!-- In recent years, inductive research has been gaining traction as a technique to complement existing theories by identifying important omissions[2]. In particular, machine learning offers powerful new tools for systematic exploration that can identify relevant predictors and complex relationships that have eluded theoreticians[5]. Machine learning is an approach to data analysis that focuses on maximizing predictive performance. This involves the use of flexible models to find reliable patterns in data. Machine learning models can distill a large set of candidate variables down to the ones that are most important in predicting the outcome of interest, and also indicate the direction and shape of the marginal association between those predictors and the outcome. In a context where predictor variables are likely to be related to each other, machine learning is better suited to manage these complex relationships than, e.g., multiple regressions. Moreover, it incorporates checks and balances to prevent spurious findings [3]. -->

<!-- The field of adolescent emotion regulation is prolific, but lacks overarching theory. -->
<!-- For guidance on how to remedy this shortcoming, we turn to philosophy of science. -->
<!-- De Groot’s "empirical cycle" constitutes a model of the production of knowledge through scientific research [@degrootMethodologieGrondslagenVan1961]. -->
<!-- It consists of five phases: *observation* of phenomena to be explained; *induction* of hypotheses; *deduction* or derivation of testable predictions; *testing* these predictions in new data; and finally *evaluation*: reflecting back on the theories and hypotheses that gave rise to the tested predictions. -->
<!-- The model is cyclical because *evaluation* offers new interpretative data for the researcher to observe - such as rejected hypotheses and serendipitous findings. -->

<!-- The empirical cycle is merely one model, -->
<!-- and there is a pluriformity of other epistemological approaches to knowledge production. -->
<!-- Nonetheless, u -->
<!-- Unsubstantiated or undisclosed deviations from the empirical cycle may signal practices that limit scientific progress. -->
<!-- Consider three examples: -->
<!-- First, conducting many analyses and then writing a paper that presents significant findings as tests of a-priori hypotheses, or "hypothesizing after the results are known", constitutes a questionable research practice that leads to false-positive results [@wichertsDegreesFreedomPlanning2016]. -->
<!-- Second, failure to engage in evaluation and reflect back on theory in light of empirical findings leads to flexible, "invulnerable" theories that can accommodate any result [@szollosiArrestedTheoryDevelopment2021]. -->
<!-- Third, and particularly relevant to the present study, -->
<!-- is failure to complete the cycle. -->
<!-- In a productive field of study, the empirical cycle is regularly completed; -->
<!-- evaluation of theories in the light of empirical findings allows scholars to hone those theories, -->
<!-- which in turn yield increasingly precise predictions. -->
<!-- We argue that, the paucity of overarching theory in our field can be remedied by completing the empirical cycle. -->

<!-- The phases of the empirical cycle map onto two modes of conducting research: -->
<!-- Confirmatory research, which involves the phases of deduction, testing, and evaluation, and exploratory research, which involves the phases of observation and induction  [@wagenmakersCreativityVerificationCyclePsychological2018]. -->
<!-- Although developmental psychology is dominated by quantitative positivism, -->
<!-- relatively few studies are explicitly exploratory [@demuthQualitativeMethodologyDevelopmental2015]. -->
<!-- There are two main indications that some studies are implicitly exploratory. -->

<!-- The first is that some, apparently confirmatory, papers are not rooted in any theoretical framework, but instead based exclusively on prior empirical literature. -->

<!-- The second indication is that an increasing number of studies use complex modeling techniques in the absence of theory specific enough to derive hypotheses for such models. -->
<!-- For example, consider the recent literature using the random-intercept cross-lagged panel model, -->
<!-- a complex structural equation model that separates stable differences between individuals from processes within  individuals (or families). -->
<!-- Several authors have remarked that theory in their areas of expertise is insufficiently precise to derive specific and distinct predictions about effects at the between- and within level. -->
<!-- At first glance, these publications fit the mold of confirmatory research, providing hypotheses and tests thereof. -->
<!-- Upon further reflection, the hypotheses tested are not very specific (e.g., specifying a positive relation between two constructs, regardless of level of analysis), -->
<!-- and they can be simultaneously supported and refuted by different parameters in the model without repercussions for theory. -->
<!-- They are thus not truly "testable" in the sense that De Groot intended. -->
<!-- Furthermore, the focus in these publications is on post-hoc interpretation of many parameter estimates - a hallmark of exploratory research. -->
<!-- Implicitly exploratory research such as this suggests that others have perceived the need for more exploration, -->
<!-- but that exploratory work is wrt as confirmatory the exploratory mode of research is not ingrained in the field. -->

<!-- have noted that existing theory is insufficiently specific  -->
<!-- ,  -->

<!-- and devoting greater attention to exploratory research and theory formation. -->

<!-- In this model, the hypothesis plays an important role. -->
<!-- It is a testable prediction that can be supported or falsified; depending on the results, we reflect on old knowledge – which includes theory – and make necessary adjustments that lead to new hypotheses. -->
<!-- A hypothesis can thus be a specific prediction that delivers new knowledge when it is false; -->
<!-- this drives a scientific field forward. -->

<!-- Prior theory and empirical research thus suggests many phenomena potentially related to heterogeneity in adolescents' emotion regulation development. -->
<!-- What is missing is an understanding of the relative utility of each of these phenomena in predicting developmental outcomes. -->
<!-- Individual studies do not suffice for this purpose as -->
<!-- they tend to sample from different populations, -->
<!-- use different research designs, -->
<!-- different control variables and statistical models. -->
<!-- Relatedly, many studies tend to examine only a handful of predictors, -->
<!-- often guided by a theory with narrow scope -  -->
<!-- , it is hard to tell how important the variables are, relative to other variables considered by other theories (or variables not considered at all). Machine learning is a more holistic methodology, as it can assess and compare a large number of potential predictors simultaneously, including theoretically relevant ones, and identify which predictors ultimately explain the most variance in the outcome measure of interest -->

<!--   Machine learning is a more holistic methodology, as it can assess and compare a large number of potential predictors simultaneously, including theoretically relevant ones, and identify which predictors ultimately explain the most variance in the outcome measure of interest. -->

<!-- Theory cons methods for theory construction state that the first step in this endeavor is to identify well-established relevant *empirical phenomena*, -->
<!-- defined as stable and general features of the world [@borsboomTheoryConstructionMethodology2020]. -->
<!-- The current study used a text mining systematic review to provide a comprehensive map of the empirical phenomena relevant to adolescent emotion regulation. -->

<!-- Currently, few instruments exist for the identification of relevant phenomena; instead, theorists typically rely on expert opinion [@borsboomTheoryConstructionMethodology2020]. -->
<!-- This paper argues that systematic reviews are a suitable and relatively more objective method for phenomena detection. -->
<!-- Traditional narrative reviews are limited, however, by small convenience samples, -->
<!-- confirmation bias, -->
<!-- and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. -->
<!-- These limitations are overcome by a novel method: -->
<!-- the text mining systematic review (TMSR). -->
<!-- Relative to narrative reviews, text mining can cover arbitrarily greater corpora, -->
<!-- and gleans insights from the literature by means of a relatively more transparent, objective, and reproducible process. -->
<!-- <!--Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008], -->
<!-- the inherent "fairness" of text mining gives emerging themes a chance to come to the fore.--> -->
<!-- This approach assumes the frequency with which phenomena recur in the literature to be indicative of their relevance. -->
<!-- If it is additionally assumed that the frequency with which phenomena are studied together is indicative of the extent to which they are thought to be associated, -->
<!-- then the co-occurrence of phenomena within publications can be interpreted as a rudimentary nomological network: a mapping of relationships between theoretically relevant phenomena [see @alaviAligningTheoryMethodology2018]. -->
<!-- Such a network can serve as a starting point for the formulation of a proto-theory, -->
<!-- which would additionally involve abductive reasoning: specifying putative mechanisms to explain associations between the phenomena [@borsboomTheoryConstructionMethodology2020]. -->
<!-- Text mining systematic reviews constitute an inductive and exploratory approach: -->
<!-- Their aim is phenomena detection based on generalization from observations (data) without appeal to theory [@haigExploratoryFactorAnalysis2005]. -->
<!-- By identifying and mapping the phenomena relevant to adolescent emotion regulation, -->
<!-- such an inductive approach lays the groundwork for future theory development. -->

<!--
stifterEmotionRegulation2019
* call for studies incorporating predictors of ER across multiple levels of analysis
* different conceptual frameworks

riedigerEmotionRegulationAdolescence2014
* difficulty in deriving a cohesive picture about emotion regulation in adolescence
* different conceptual frameworks

* three themes (neurocognitive development, socialization, interplay between internal and external factors) currently represent relatively independent bodies of research
* A more explicit integration of these various research perspectives will help us to arrive at a more integrated and interpretable picture of the development of emorion regulation during adolescence.

@bussTheoriesEmotionalDevelopment2019

* emotional development theory is still in its own state of development. 
* empirical evidence can contribute to theory development.

@bariolaChildAdolescentEmotion2011
* Further research apply reﬁned theoretical conceptualizations of ER.

Where sentient readers tend to structure their reading of the literature around established ideas [@littellEvidencebasedBiasedQuality2008],
This potentially reveals phenomena and associations missed by narrative reviewers,
thereby laying the groundwork for future empirical and theoretical work.

we set out to map these relevant empirical phenomena using a systematic review.

generate a proto-theoretical nomological network of the relevant empirical phenomena.
We discuss how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.
There have been calls for the  consolidation of these disparate insights into overarching theory would be an important step forward.
An important first step 
and intrinsic limitations of narrative reviews prohibit comprehensive coverage of the vast but diffuse literature .-->
<!--
Recent years have seen the publication of several excellent systematic reviews,
but these have all been narrative reviews.-->

 <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->
<!-- At the same time, the staggered development of motivational-emotional and regulatory brain circuits gives rise
to a maturity gap [@croneUnderstandingAdolescencePeriod2012]. 
This leads youngsters to pursue new experiences in life and love,
without being fully prepared to cope with the emotional outcomes. -->

<!--The literature thus paints a picture of
adolescence as a chrysalis for emotional development: Children enter this stage
with emotion regulation skills adapted to the challenges of childhood. During
adolescence, emotional systems are rearranged substantially.-->

<!--
* intense negative emotions in daily life (Silk, Steinberg, & Morris, 2003) 
* unstable peer or romantic relationships (Furman & Collins, 2009)
* decrease in perceived support from parents (Furman & Buhrmester, 1992).
* early adolescence is characterized by a higher rate of conflicts with parents (Laursen, Coy, & Collins, 1998)
* higher variability of negative emotions compared to late adolescence (Larson, Moneta, Richards, & Wilson, 2002).
* relative to other developmental stages, adolescence involves a particularly large number of transitions, novel situations, and new stimuli, physical, cognitive, emotional, and social development—particularly in early and mid-adolescence (Seiffge-Krenke, 2000)
-->

<!-- ## Knowledge gap -->

<!-- Substantial empirical research, but: -->

<!-- * Different (sub)disciplines have approached the topic in disparate ways [@riedigerEmotionRegulationAdolescence2014] -->
<!-- * No consistent terminology [@bariolaChildAdolescentEmotion2011] -->
<!-- * No conceptual frameworks [@stifterEmotionRegulation2019] -->
<!-- * No overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019] -->

<!-- Knowledge must be consolidated into overarching theory -->

## Method

@@

Predictors: 87

Categories:

* Demographics (e.g., SES)
* Biological (age, sex, pubertal development)
* Individual differences (big5, BIS/BAS, empathy)
* Risk behavior (in/externalizing symptoms, substance use, delinquency, school performance, victimization)
* Relationship quality (parents/peers)
* Parenting (perceived and parent-reported)
* Conflict resolution styles

Difficulties in emotion regulation [@gratzMultidimensionalAssessmentEmotion2004]

* 24 items (omitted 'emotional awareness' subscale)
* E.g.: “When I’m upset, I have difficulty thinking about anything else”
* 1 (“Almost never”) to 5 (“Almost always”)
* Excellent reliability, $(.94 > \alpha > .95)$.
* Metric invariance across waves
* Quadratic growth model had good fit
  + CFI = .996, TLI = .993, RMSEA = .047, SRMR = 0.020

## Open science

Workflow for Open Reproducible Code in Science (WORCS) used to make analyses reproducible [@vanlissaWORCSWorkflowOpen2020]

All code and synthetic data available at

<https://github.com/cjvanlissa/veni_forest>

@@

>>>>

---
title             : "Complementing theory on adolescent emotion regulation using data-driven insights from machine learning"
shorttitle        : "Emotion Regulation and Machine Learning"

@@

```{r setup, include = FALSE}
library("papaja")
library("worcs")
library(tidySEM)
options(knitr.kable.NA = '')

```

@@

Empirical support for this notion of diverging destinies is evident from studies that examine developmental trajectories of emotion regulation in adolescence: 
Such studies consistently reveal large between-individual heterogeneity [see @craccoEmotionRegulationChildhood2017; @vanlissaRoleFathersMothers2019; @zimmermannEmotionRegulationEarly2014; @reindlSocializationEmotionRegulation2016].
An important next step is to identify which risk factors render some adolescents susceptible to emotion dysregulation.
<!-- This goal fits within the paradigm shift that has gripped the field of pedagogy, towards "person-centered" research, which focuses on individual developmental trajectories and within-family predictive processes, rather than average patterns across samples16,23. Seminal studies have applied "clustering" methods to identify youth with similar developmental trajectories14,24–26. Adolescents may follow similar trajectories for different reasons, however, and person-centered methods are too complex to accommodate more than a handful of theoretically-derived predictors. Unfortunately, relevant theory on adolescent emotion regulation development is limited27–29. The field is therefore at an impasse: We know that some adolescents are more susceptible to emotion dysregulation than others, but lack tools and theory to identify important predictors of individual development30. -->

@@

<!-- Maybe review theory briefly? -->
The first step towards theory formation or revision is identifying relevant phenomena [@borsboomTheoryConstructionMethodology2020].
<!--Thus, offering a starting point for this endeavor,<!-- empirical investigations of predictors of adolescents' emotion regulation development -->
A recent literature review did so
using a text mining systematic review of author keywords and abstracts of 6305 publications on  adolescents’ emotion regulation [@vanlissaMappingPhenomenaRelevant2021].
Typically, phenomena are identified using narrative literature reviews.
However, these are often limited to a small number of papers and structured around well-established ideas [@littellEvidencebasedBiasedQuality2008]
Text mining systematic reviews, by comparison, are relatively comprehensive and derive insights from the literature through a relatively transparent and objective - albeit less interpretative - procedure [@vanlissaMappingPhenomenaRelevant2021]. <!-- reflection and meaning-making-->

@@

# Method

The Workflow for Open Reproducible Code in Science (WORCS) was used to make analyses reproducible [@vanlissaWORCSWorkflowOpen2020].
All analysis code, supplemental materials and synthetic data are available at <https://github.com/cjvanlissa/veni_forest>.
The original data (restricted) and all study documentation are available via <https://doi.org/10.17026/DANS-ZRB-V5WP>.

## Participants

```{r}
desc_num <- read.csv("../desc_num.csv", stringsAsFactors = FALSE)
desc_cat <- read.csv("../desc_cat.csv", stringsAsFactors = FALSE)
```
Participants were 497 Dutch adolescents and their parents enrolled in the longitudinal RADAR study  [@branjeResearchAdolescentDevelopment2018].
The RADAR sample was recruited from randomly selected elementary schools in the province of Utrecht, and four main cities in The Netherlands.
Of 1,544 randomly selected families, 497 produced informed consent and were included in the study.
From 2006 to 2012, trained interviewers conducted annual home visits to collect questionnaire data from adolescents and parents.
All independent variables were assessed in the first measurement wave.
The dependent variable was measured from the second to the sixth wave.
Adolescents received financial compensation for their participation in annual measurements (approximately \$17).

## Measures

```{r}
ders_desc <- readRDS("../ders_desc.RData")
alphs <- sapply(ders_desc, function(x){x$alpha$total$raw_alpha})
```

From wave 2-6, adolescents completed the difficulty in emotion regulation scale [DERS, @gratzMultidimensionalAssessmentEmotion2004].
Based on prior psychometric analyses [see @vanlissaRoleFathersMothers2018],
we used 24 items of this 32-item scale
(e.g., "When I’m upset, I have difficulty thinking
about anything else").
Responses ranged
from 1 (Almost never) to 5 (Almost always).
Reliability was excellent in all waves, $\alpha \in [`r report(min(alphs), equals = F)`, `r report(max(alphs), equals = F)`]$.
According to confirmatory factor analyses,
a model that imposed metric measurement invariance across waves ($BIC = 140913.27$) was preferable over a model with configural invariance ($BIC = 141247.46$).
The RMSEA and SRMR of this model indicated acceptable fit ($\text{RMSEA} = .05, \text{SRMR} = 0.05$), but the CFI indicated poor fit ($\text{CFI} = .80$).
However, as reliability and standardized factor loadings ($\lambda \in [0.44, 0.84]$) were high across all waves, we extracted individual factor scores for further analysis.
As quadratic growth model fit to the full sample had excellent fit, $\text{RMSEA} < .05, \text{SRMR} = 0.02, \text{CFI} = 1.00$.

We set out to identify operationalizations of all relevant phenomena identified in @vanlissaMappingPhenomenaRelevant2021 that were available in the RADAR data.
This yielded 87 candidate predictors, of which `r nrow(desc_cat)` categorical (see Table \@ref(tab:tabcat)), `r sum(is.na(desc_num$Items))` numerical, and `r sum(!is.na(desc_num$Items))` multi-item scales, see \@ref(tab:tabcont).
We used principal components analysis for dimension reduction of multi-item scales.
Across all scales, the explained variance of the first component ranged from $R^2 \in [0.18, 0.90]$.
Supplementary Table S1 additionally reports skew and kurtosis,
the minimum and maximum factor loading of a CFA fit to each scale,
sample items,
and references to the scale validation papers.

```{r tabcat, results='asis'}
papaja::apa_table(desc_cat, caption = "Sample descriptive statistics for categorical predictors.", format.args = list(na_string = ""))
```
```{r tabcont, results='asis'}
 options(knitr.kable.NA = '')
papaja::apa_table(desc_num[,c("name", "n", "Items", "mean", "sd", "min", "max", "Reliability", "PC1")
], caption = "Sample descriptive statistics for continuous variables and scales.", landscape = FALSE, longtable = TRUE, format.args = list(na_string = ""))
```

## Strategy of analyses

<!-- Our analyses were based on an extension of cross-lagged panel modeling (Selig & Little, 2012), with staggered measurement occasions for one of the variables (mood variability). Mood variability was measured each time during the year between two measurement waves. Thus, for mood variability, no within-wave correlations were estimated, and all links with conflict frequency and difficulties in emotion regulation were specified as (predictive) regression paths. We used this staggered cross-lagged panel model to investigate over-time predictive effects between conflict frequency, day-to-day mood variability, and difficulties in emotion regulation. First, we estimated a single-group path model with autoregressive and cross-lagged paths, as well as within-time correlations for concurrent measurements (Model 1, see Table 1). Then we introduced empathy (high, average, low) as a moderator in a multi-group model, with all parameters free to vary between groups (Model 2). To derive the best fitting, most parsimonious model, we constrained parameters that were not significantly different. We used Wald \chi^2 tests to evaluate which parameters did not differ significantly, first over time and then between groups. We used the resulting final model to test our hypotheses (Model 3, see Figure 2). For hypotheses involving moderation, we used Wald tests to investigate whether parameters differed significantly between empathy groups. To test hypotheses involving mediation, we inspected indirect effects with bootstrapped standard errors (10,000 resamples). Furthermore, although posterior predictive probabilities were high, we conducted additional analyses, using the approach described by Asparouhov and Muthén (2014) to account for classification uncertainty. As can be seen in Appendix A, results were in line with the multi-group model reported here. -->
<!-- Attrition for the annual measurements ranged from 0.40% at age 13 to 14.50% at age 18, and attrition for the daily mood diaries ranged from 3.40% to 23.40%. These data were missing completely at random, Little’s (1988) MCAR test \chi^2(2179) = 2124.07, p = .80. Therefore, full information maximum likelihood estimation (FIML) was warranted to make use of all available information without estimating missing data. All analyses were conducted in Mplus Version 7 (Muthén & Muthén, 1998–2012). Per the developers’ recommendation, we used robust maximum-likelihood estimation, which yields a Satorra-Bentler scaled \chi^2 value to account for potential non-normality (Satorra, 2000). Model fit was evaluated using the Comparative Fit Index and Tucker–Lewis Index (CFI and TLI, acceptable fit = 0.90-0.95, Bentler & Bonett, 1980), and Root Mean Square Error of Approximation (RMSEA, close fit = 0.01-0.06, acceptable fit = 0.06-0.08, Browne & Cudeck, 1993). According to these criteria, the fit of the final model was acceptable-to-good (Table 1). In addition to these measures of objective fit, we also provide two comparative fit indices, the Akaike Information Criterion (AIC) and sample-size adjusted Bayesian Information Criterion (saBIC). Lower values on these comparative fit indices indicate a better fitting model. According to both relative and absolute fit indices, the final model had the best fit. -->

@@

@@

<!-- Categories:  -->

<!-- * Demographics (e.g., SES) -->
<!-- * Biological (age, sex, pubertal development) -->
<!-- * Individual differences (big5, BIS/BAS, empathy) -->
<!-- * Risk behavior (in/externalizing symptoms, substance use, delinquency, school performance, victimization) -->
<!-- * Relationship quality (parents/peers) -->
<!-- * Parenting (perceived and parent-reported) -->
<!-- * Conflict resolution styles -->
